---
title: "Errata for Flores and Coppock (2018)"
subtitle: "Do Bilinguals Respond More Favorably to Candidate Advertisements in English or in Spanish?"
format:
  pdf:
    output-file: flores_coppock_2018_errata.pdf
    geometry: margin=1.2in
    fontsize: 11pt
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(here)
library(tidyverse)

here::i_am("errata.qmd")

# Every corrected value below is computed here rather than typed. The outcome scales
# come from the pipeline's own reading of the deposited data; the appendix section
# letters come from the extraction of the appendix's contents page.
facts <- read_csv(here::here("maintained", "output", "text_design_facts.csv"),
                  show_col_types = FALSE)
published_claims <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)

fact <- function(name) {
  value <- facts$value[facts$quantity == name]
  stopifnot(length(value) == 1)
  value
}

appendix_sections <- published_claims |>
  filter(str_starts(claim_id, "appendix_section_")) |>
  transmute(letter = str_to_upper(str_remove(claim_id, "^appendix_section_")),
            title = str_remove(str_remove(claim, ",.*"), "^[A-E] "))

# The two control means the first entry cites are published values, so they come from
# the transcription of the article's tables rather than from this document.
published_values <- read_csv(here::here("ground_truth", "published_values.csv"),
                             col_types = cols(.default = col_character()))

published_cell <- function(tab, col, stat) {
  value <- published_values$value_paper[published_values$table_figure == tab &
                                          published_values$column == col &
                                          published_values$stat == stat]
  stopifnot(length(value) == 1)
  value
}

section_letter <- function(title) {
  hit <- appendix_sections |> filter(str_detect(title, fixed(.env$title)))
  stopifnot(nrow(hit) == 1)
  hit$letter
}

section_title <- function(letter) {
  hit <- appendix_sections |> filter(.data$letter == .env$letter)
  stopifnot(nrow(hit) == 1)
  hit$title
}

confidence_low <- fact("conf_in_bush_min")
confidence_high <- fact("conf_in_bush_max")
linked_fate_low <- fact("linked_fate_min")
linked_fate_high <- fact("linked_fate_max")

quiz_letter <- section_letter("Language Quiz")
survey_letter <- section_letter("Spanish-Language Survey")
logit_letter <- section_letter("Binary Choice Models")
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Both entries here correct several sentences at once, so published and
# corrected carry one block per corrected sentence, separated by a blank line and paired
# off in order.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "definition", "pipeline", "full",
  "Two outcome scales are described as running from 1 to 4 and are analysed as running from 0 to 3",
  "published, Outcome Measures",
  str_c(
    "Confidence in Candidate: \"How confident are you in [Candidate]'s ability to make the right decisions about illegal immigration? Are you very confident, somewhat confident, not too confident, or not at all confident?\" [Scale from [[1 to 4]], where [[4]] indicates greater confidence]",
    "\n\n",
    "Linked Fate: \"Do you think that what happens generally to Hispanics and Latinos in this country will have something to do with what happens in your life? Will it affect you a lot, some, a little or not at all?\" [Scale from [[1 to 4]], where [[4]] indicates \"a lot\"]"),
  str_c(
    str_glue("Confidence in Candidate: \"How confident are you in [Candidate]'s ability to make the right decisions about illegal immigration? Are you very confident, somewhat confident, not too confident, or not at all confident?\" [Scale from [[{confidence_low} to {confidence_high}]], where [[{confidence_high}]] indicates greater confidence]"),
    "\n\n",
    str_glue("Linked Fate: \"Do you think that what happens generally to Hispanics and Latinos in this country will have something to do with what happens in your life? Will it affect you a lot, some, a little or not at all?\" [Scale from [[{linked_fate_low} to {linked_fate_high}]], where [[{linked_fate_high}]] indicates \"a lot\"]")),
  str_glue(
    "The confidence and linked fate variables in the replication data take the values ",
    "{str_flatten_comma(seq(confidence_low, confidence_high))} and are analysed on that ",
    "scale, so the control means the article reports for them are on a {confidence_low}-to-",
    "{confidence_high} scale as well: {published_cell('table_8', 'bush_bilingual', 'constant')} ",
    "for confidence in Bush in Table 8 and ",
    "{published_cell('table_9', 'bush_bilingual', 'constant')} for linked fate in Table 9. ",
    "The three other outcome measures are described correctly. A shift of the scale leaves ",
    "every treatment effect unchanged, so no estimate in Tables 8 or 9, in appendix Tables ",
    "A.3 or B.8, or in Figures 1 or 2 is affected; what the correction changes is how a ",
    "reader should read the constants. Appendix D restates both brackets in the Spanish ",
    "version of the questionnaire and takes the same correction."),

  2, "cross_reference", "pipeline", "full",
  "Three references to a lettered appendix section name the wrong section",
  "published, main text",
  str_c(
    "In our first experiment (Bush), we collected responses from 2,866 self-identified Latinos, of which 1,862 passed a language quiz in both Spanish and English, the full text of which is presented in the supplemental Appendix [[D]].",
    "\n\n",
    "We present the English-language versions here; subjects assigned to the Spanish-language survey saw these questions in Spanish, the full text of which is available in the supplemental Appendix [[C]].",
    "\n\n",
    "Our substantive results do not depend on this choice (see supplemental Appendix [[A]] for logistic regression tables equivalent to Tables 5 and 7)."),
  str_c(
    str_glue("In our first experiment (Bush), we collected responses from 2,866 self-identified Latinos, of which 1,862 passed a language quiz in both Spanish and English, the full text of which is presented in the supplemental Appendix [[{quiz_letter}]]."),
    "\n\n",
    str_glue("We present the English-language versions here; subjects assigned to the Spanish-language survey saw these questions in Spanish, the full text of which is available in the supplemental Appendix [[{survey_letter}]]."),
    "\n\n",
    str_glue("Our substantive results do not depend on this choice (see supplemental Appendix [[{logit_letter}]] for logistic regression tables equivalent to Tables 5 and 7).")),
  str_glue(
    "Each of the three sends the reader to a section holding different material: Appendix D ",
    "is {section_title('D')}, Appendix C is {section_title('C')}, and Appendix A is ",
    "{section_title('A')}. The article's two other references, to Appendix A for the ",
    "interaction specifications and to Appendix B for the partisanship tables, resolve ",
    "correctly, as does the cross-reference from appendix section C to Tables 5 and 7.")
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
blocks <- function(x) str_split_1(x, "\n\n")

# The count of entries is read off the spine rather than typed, and the note spells it out.
spell <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")
  stopifnot(n >= 1, n <= length(words))
  words[n]
}

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one.
emit <- function(n, lead) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n", lead, "\n\n", sep = "")
  walk2(blocks(e$published), blocks(e$corrected), function(was, now) {
    cat("> ", bold(was), "\n\n**Corrected:** ", bold(now), "\n\n", sep = "")
  })
  cat(e$note, "\n", sep = "")
}
```

`r glue::glue("This note corrects {spell(nrow(entries))} errors in Flores, A. and Coppock, A. (2018), \"Do bilinguals respond more favorably to candidate advertisements in English or in Spanish?\", *Political Communication* 35(4), 612-633, doi [10.1080/10584609.2018.1426663](https://doi.org/10.1080/10584609.2018.1426663). Neither changes any estimate, any table or figure, or any conclusion of the article. Every corrected value is computed at render time from the maintained replication code at [github.com/active-maintenance-aec/flores_coppock_2018](https://github.com/active-maintenance-aec/flores_coppock_2018), which reproduces all {nrow(published_values)} numbers printed in the article's and the appendix's tables.")`

Changed text is shown in bold on both sides of each correction.

```{r entry-1, results="asis"}
emit(1, "The Outcome Measures section describes the coding of each dependent variable. Two of the five brackets state the wrong endpoints.")
```

```{r entry-2, results="asis"}
emit(2, glue::glue("The appendix's contents page lists {str_flatten_comma(paste0(appendix_sections$letter, ' ', appendix_sections$title))}. Three of the article's five references to a lettered section point elsewhere."))
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
