---
title: "Errata for Flores and Coppock (2018)"
subtitle: "Do Bilinguals Respond More Favorably to Candidate Advertisements in English or in Spanish?"
format:
  pdf:
    output-file: flores_coppock_2018_errata.pdf
    geometry: margin=1.2in
    fontsize: 11pt
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(here)
library(tidyverse)

here::i_am("errata.qmd")

# Every corrected value below is computed here rather than typed. The outcome scales
# come from the pipeline's own reading of the deposited data; the appendix section
# letters come from the extraction of the appendix's contents page.
facts <- read_csv(here::here("maintained", "output", "text_design_facts.csv"),
                  show_col_types = FALSE)
published_claims <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)

fact <- function(name) {
  value <- facts$value[facts$quantity == name]
  stopifnot(length(value) == 1)
  value
}

appendix_sections <- published_claims |>
  filter(str_starts(claim_id, "appendix_section_")) |>
  transmute(letter = str_to_upper(str_remove(claim_id, "^appendix_section_")),
            title = str_remove(str_remove(claim, ",.*"), "^[A-E] "))

# The two control means the first entry cites are published values, so they come from
# the transcription of the article's tables rather than from this document.
published_values <- read_csv(here::here("ground_truth", "published_values.csv"),
                             col_types = cols(.default = col_character()))

published_cell <- function(tab, col, stat) {
  value <- published_values$value_paper[published_values$table_figure == tab &
                                          published_values$column == col &
                                          published_values$stat == stat]
  stopifnot(length(value) == 1)
  value
}

section_letter <- function(title) {
  hit <- appendix_sections |> filter(str_detect(title, fixed(.env$title)))
  stopifnot(nrow(hit) == 1)
  hit$letter
}

section_title <- function(letter) {
  hit <- appendix_sections |> filter(.data$letter == .env$letter)
  stopifnot(nrow(hit) == 1)
  hit$title
}

confidence_low <- fact("conf_in_bush_min")
confidence_high <- fact("conf_in_bush_max")
linked_fate_low <- fact("linked_fate_min")
linked_fate_high <- fact("linked_fate_max")

quiz_letter <- section_letter("Language Quiz")
survey_letter <- section_letter("Spanish-Language Survey")
logit_letter <- section_letter("Binary Choice Models")
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Both entries here correct several sentences at once, so published and
# corrected carry one block per corrected sentence, separated by a blank line and paired
# off in order.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
#
# claim_ids names the ground-truth rows an entry corrects, semicolon-separated, so that
# "is this finding published?" is a query rather than a judgment. It is empty for entries 3
# to 13: a misspelling and a mangled reference-list entry are not extraction claims, so no
# ground-truth row exists to name. Every id listed here is checked against the ground truth
# by build_ground_truth.R.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "definition", "pipeline", "full",
  "Two outcome scales are described as running from 1 to 4 and are analysed as running from 0 to 3",
  "published, Outcome Measures",
  str_c(
    "Confidence in Candidate: \"How confident are you in [Candidate]'s ability to make the right decisions about illegal immigration? Are you very confident, somewhat confident, not too confident, or not at all confident?\" [Scale from [[1 to 4]], where [[4]] indicates greater confidence]",
    "\n\n",
    "Linked Fate: \"Do you think that what happens generally to Hispanics and Latinos in this country will have something to do with what happens in your life? Will it affect you a lot, some, a little or not at all?\" [Scale from [[1 to 4]], where [[4]] indicates \"a lot\"]",
    "\n\n",
    "(Scale from [[1 to 4]], where [[4]] indicates greater confidence.)",
    "\n\n",
    "(Scale from [[1 to 4]], where [[4]] indicates \"a lot.\")"),
  str_c(
    str_glue("Confidence in Candidate: \"How confident are you in [Candidate]'s ability to make the right decisions about illegal immigration? Are you very confident, somewhat confident, not too confident, or not at all confident?\" [Scale from [[{confidence_low} to {confidence_high}]], where [[{confidence_high}]] indicates greater confidence]"),
    "\n\n",
    str_glue("Linked Fate: \"Do you think that what happens generally to Hispanics and Latinos in this country will have something to do with what happens in your life? Will it affect you a lot, some, a little or not at all?\" [Scale from [[{linked_fate_low} to {linked_fate_high}]], where [[{linked_fate_high}]] indicates \"a lot\"]"),
    "\n\n",
    str_glue("(Scale from [[{confidence_low} to {confidence_high}]], where [[{confidence_high}]] indicates greater confidence.)"),
    "\n\n",
    str_glue("(Scale from [[{linked_fate_low} to {linked_fate_high}]], where [[{linked_fate_high}]] indicates \"a lot.\")")),
  str_glue(
    "The confidence and linked fate variables in the replication data take the values ",
    "{str_flatten_comma(seq(confidence_low, confidence_high))} and are analysed on that ",
    "scale, so the control means the article reports for them are on a {confidence_low}-to-",
    "{confidence_high} scale as well: {published_cell('table_8', 'bush_bilingual', 'constant')} ",
    "for confidence in Bush in Table 8 and ",
    "{published_cell('table_9', 'bush_bilingual', 'constant')} for linked fate in Table 9. ",
    "The three other outcome measures are described correctly. A shift of the scale leaves ",
    "every treatment effect unchanged, so no estimate in Tables 8 or 9, in appendix Tables ",
    "A.3 or B.8, or in Figures 1 or 2 is affected; what the correction changes is how a ",
    "reader should read the constants. The last two quotations above are the same two ",
    "brackets as they are restated in appendix section D, beside the Spanish version of ",
    "each question; they take the same correction."),
  str_c("design_confidence_min;design_confidence_max;design_confidence_top;",
        "design_linked_fate_min;design_linked_fate_max;design_linked_fate_top"),

  2, "cross_reference", "pipeline", "full",
  "Three references to a lettered appendix section name the wrong section",
  "published, main text",
  str_c(
    "In our first experiment (Bush), we collected responses from 2,866 self-identified Latinos, of which 1,862 passed a language quiz in both Spanish and English, the full text of which is presented in the supplemental Appendix [[D]].",
    "\n\n",
    "We present the English-language versions here; subjects assigned to the Spanish-language survey saw these questions in Spanish, the full text of which is available in the supplemental Appendix [[C]].",
    "\n\n",
    "Our substantive results do not depend on this choice (see supplemental Appendix [[A]] for logistic regression tables equivalent to Tables 5 and 7)."),
  str_c(
    str_glue("In our first experiment (Bush), we collected responses from 2,866 self-identified Latinos, of which 1,862 passed a language quiz in both Spanish and English, the full text of which is presented in the supplemental Appendix [[{quiz_letter}]]."),
    "\n\n",
    str_glue("We present the English-language versions here; subjects assigned to the Spanish-language survey saw these questions in Spanish, the full text of which is available in the supplemental Appendix [[{survey_letter}]]."),
    "\n\n",
    str_glue("Our substantive results do not depend on this choice (see supplemental Appendix [[{logit_letter}]] for logistic regression tables equivalent to Tables 5 and 7).")),
  str_glue(
    "Each of the three sends the reader to a section holding different material: Appendix D ",
    "is {section_title('D')}, Appendix C is {section_title('C')}, and Appendix A is ",
    "{section_title('A')}. The article's two other references, to Appendix A for the ",
    "interaction specifications and to Appendix B for the partisanship tables, resolve ",
    "correctly, as does the cross-reference from appendix section C to Tables 5 and 7."),
  str_c("design_appendix_quiz_reference;design_appendix_survey_reference;",
        "design_appendix_logit_reference"),

  # Entries 3 to 13 were found by reading every word of the published article and its
  # appendix against the published PDF while preparing the remastered edition, which is a
  # finer sieve than the pipeline: none of them is a number, so nothing in the ground
  # truth, in in_text_claims.R or in the corpus reference audit could have raised them.
  # Each bibliographic entry is verified against the authoritative record by DOI.

  3, "spelling", "reading", "brief",
  "A misspelled word in the account of the randomized language-of-contact experiments",
  "published, p. 614",
  "Binder and [[colleages]] (2013)",
  "Binder and [[colleagues]] (2013)",
  "",
  "",

  4, "spelling", "reading", "brief",
  "Figure 2's caption misspells advertisement",
  "published, p. 628",
  "Heterogeneous effects of Spanish-language [[advertisment]] on four outcomes",
  "Heterogeneous effects of Spanish-language [[advertisement]] on four outcomes",
  "",
  "",

  5, "spelling", "reading", "brief",
  "A misspelled word in note 4",
  "published, p. 631",
  "The quiz was administered [[post-treatmeant]].",
  "The quiz was administered [[post-treatment]].",
  "",
  "",

  6, "spelling", "reading", "brief",
  "A misspelled word in appendix section C",
  "supplemental appendix, p. 5",
  "we include [[logisitic]] regression tables for completeness",
  "we include [[logistic]] regression tables for completeness",
  "",
  "",

  7, "bibliographic", "crossref", "brief",
  "Both authors' names are mangled in the Soto and Merolla reference",
  "published, p. 633",
  "[[Soto, V. M., & Merolla, D. J. L.]] (2006).",
  "[[DeFrancesco Soto, V. M., & Merolla, J. L.]] (2006).",
  str_c("The authors of record for doi:10.1007/s11109-006-9012-7 are Victoria M. ",
        "DeFrancesco Soto and Jennifer L. Merolla. The publisher's reference processor ",
        "dropped DeFrancesco from the first surname and carried its initial onto the ",
        "second author's. The in-text citations follow the published surname and are ",
        "left as they stand."),
  "",

  8, "bibliographic", "crossref", "brief",
  "The first author's surname is mangled in the Lavariega Monforti reference",
  "published, p. 633",
  "[[Monforti, J. L.]], Michelson, M., & Franco, A. (2013).",
  "[[Lavariega Monforti, J.]], Michelson, M., & Franco, A. (2013).",
  str_c("The author of record for doi:10.1080/21565503.2013.842491 is Jessica Lavariega ",
        "Monforti. Lavariega is part of the surname and has been demoted to an initial. ",
        "The in-text citations follow the published surname and are left as they stand."),
  "",

  9, "bibliographic", "crossref", "brief",
  "The Mackie and Cooper reference prints a first page in place of a page range",
  "published, p. 632",
  "Journal of Personality and Social Psychology, 46(3), [[575]].",
  "Journal of Personality and Social Psychology, 46(3), [[575-585]].",
  "doi:10.1037/0022-3514.46.3.575 gives the article's pages as 575 to 585.",
  "",

  10, "bibliographic", "crossref", "brief",
  "The Rubin reference prints a first page in place of a page range",
  "published, p. 633",
  "Journal of Educational Psychology, 66(5), [[688]].",
  "Journal of Educational Psychology, 66(5), [[688-701]].",
  "doi:10.1037/h0037350 gives the article's pages as 688 to 701.",
  "",

  11, "bibliographic", "crossref", "brief",
  "The Jones-Correa reference prints an issue-level locator in place of the article's DOI",
  "published, p. 632",
  "[[doi:10.1111/ssqu.2005.86.issue-3]]",
  "[[doi:10.1111/j.0038-4941.2005.00317.x]]",
  str_c("The printed string is Wiley's identifier for the whole issue of Social Science ",
        "Quarterly and resolves to no article. The article's own DOI is given here."),
  "",

  12, "bibliographic", "publisher record", "brief",
  "The Tajfel reference gives the wrong city and the wrong publisher",
  "published, p. 633",
  "[[Cambridge, MA: CUP Archive.]]",
  "[[Cambridge, UK: Cambridge University Press.]]",
  str_c("Human Groups and Social Categories was published in 1981 by Cambridge University ",
        "Press in Cambridge, England. CUP Archive is a digitisation imprint under which ",
        "the scan is catalogued, not the book's publisher."),
  "",

  13, "bibliographic", "publisher record", "brief",
  "Both authors' names are mangled in the Valdés and Seoane reference",
  "published, p. 633",
  "[[Valdés, M., & Seoane, I. M. H.]] (1995).",
  "[[Valdés, M. I., & Seoane, M. H.]] (1995).",
  str_c("The Hispanic Market Handbook is by M. Isabel Valdés and Marta H. Seoane. The ",
        "first author's second given initial was carried onto the second author's name, ",
        "the same defect as entry 7."),
  ""
) |>
  mutate(across(c(title, published, corrected, note, claim_ids), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
blocks <- function(x) str_split_1(x, "\n\n")

# The count of entries is read off the spine rather than typed, and the note spells it out.
spell <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
             "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen")
  stopifnot(n >= 1, n <= length(words))
  words[n]
}

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one. An entry with no lead sentence prints none rather than a blank.
emit <- function(n, lead = "") {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n", sep = "")
  if (nzchar(lead)) cat(lead, "\n\n", sep = "")
  walk2(blocks(e$published), blocks(e$corrected), function(was, now) {
    cat("> ", bold(was), "\n\n**Corrected:** ", bold(now), "\n\n", sep = "")
  })
  cat(e$note, "\n", sep = "")
}
```

`r glue::glue("This note corrects {spell(nrow(entries))} errors in Flores, A. and Coppock, A. (2018), \"Do bilinguals respond more favorably to candidate advertisements in English or in Spanish?\", *Political Communication* 35(4), 612-633, doi [10.1080/10584609.2018.1426663](https://doi.org/10.1080/10584609.2018.1426663). Not one of them changes an estimate or a conclusion of the article. The first two correct how a reader should read a scale and where a cross-reference points; the rest are {spell(sum(entries$class == 'spelling'))} misspellings and {spell(sum(entries$class == 'bibliographic'))} inaccurate entries in the reference list. Every corrected value that the replication code can supply is computed at render time from the maintained code at [github.com/active-maintenance-aec/flores_coppock_2018](https://github.com/active-maintenance-aec/flores_coppock_2018), which reproduces all {nrow(published_values)} numbers printed in the article's and the appendix's tables; every bibliographic correction is verified against the cited work's own record.")`

Changed text is shown in bold on both sides of each correction.

```{r entry-1, results="asis"}
emit(1, "The Outcome Measures section describes the coding of each dependent variable. Two of the five brackets state the wrong endpoints.")
```

```{r entry-2, results="asis"}
emit(2, glue::glue("The appendix's contents page lists {str_flatten_comma(paste0(appendix_sections$letter, ' ', appendix_sections$title))}. Three of the article's five references to a lettered section point elsewhere."))
```

```{r entries-3-onwards, results="asis"}
# Everything after entry 2 was found by reading the published article word by word while
# preparing the remastered edition. Each is short enough to speak for itself.
walk(entries$entry[entries$entry > 2], emit)
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
